---
title: "Coursework"
output: html_document
---


```{r}
library(httr)
library(rvest)
library(purrr)
library(dplyr)
library(ggplot2)
library(magrittr)
library(lubridate)
library(stringr)
library(viridis)
library(leaflet)
library(htmltools)
library(tibble)
library(devtools)
library(jsonlite)
```

Loading Files    


```{r}
options(stringsAsFactors = FALSE)

LiverpoolPostcodes = read.csv("Lpost.csv", header = TRUE)

LiverpoolPostcodesTrimmed <- LiverpoolPostcodes %>% dplyr::select(postcode = Postcode,lat = Latitude, long = Longitude, dist = District, ward = Ward)

LivPostcodesOnly <- LiverpoolPostcodesTrimmed[- grep("Liverpool", LiverpoolPostcodesTrimmed$dist, invert = TRUE),]

LST <- sample_n(LivPostcodesOnly, 30)
```

```{r}
crimeMonths <- str_sub(seq(ymd('2017-12-01'), ymd('2018-12-01'),
                           by = 'month'),
                       start = 1, end = 7)
```

```{r}
crimeData <- function(lat, long, date, ward) {
  
  Sys.sleep(0.1)
  
  actualURL <- "https://data.police.uk/api/crimes-street/all-crime"
  policeURL <- paste0(actualURL, "?", "lat=", lat, "&lng=", long, "&date=", date)  
  policeData <- GET(policeURL)
  
  
  jsonPoliceData <- content(policeData, "text")
  overallPoliceCrimeData <- fromJSON(jsonPoliceData, flatten = TRUE) %>% 
    mutate(location = ward)
  
  return(overallPoliceCrimeData)
}
```
 

```{r}
finalCrimeData<-data.frame()
for(i in 1:length(crimeMonths)){
 
  policeDataFinalList <- pmap(list(lat = LST$lat,
                              long = LST$long,
                              ward = LST$ward,
                              date = crimeMonths[i]),
                              crimeData)
  
  
  preFinalCrimeData <- bind_rows(policeDataFinalList) 
  
  finalCrimeData <- bind_rows(finalCrimeData, preFinalCrimeData)
  
}
```
```{r}
finalCrimeData <- finalCrimeData %>% 
    left_join(LST, by = c("location" = "ward")) %>%
    rename(date = month,
         search_lat = lat,
         search_long = long)
```

```{r}
head(finalCrimeData)
```


```{r}
finalCrimeData2 <- finalCrimeData
finalCrimeData3 <- finalCrimeData
table(finalCrimeData3$location, finalCrimeData3$date)
```



```{r}
crimeGrid <- finalCrimeData %>%
  unique() %>% 
  group_by(location, date) %>% 
  summarise(numberOfCrimes = n())
```


```{r}

ggplot(crimeGrid,aes(x=date,y=location, fill=numberOfCrimes))+
  
  geom_tile(colour="gray",size=0.5)+
  labs(x="",y="")+
  
  scale_y_discrete(expand=c(0,0))+
  
  scale_x_discrete(expand=c(0,0), 
                   breaks=c("2018-01","2018-04", "2018-07", "2018-10","2018-12"))+
  scale_fill_viridis(option = "B", name = "Number of crimes") +
  ggtitle("Number of crimes in Liverpool district's") +
  coord_fixed()+
  
  theme_grey(base_size=9)+
  
  theme(
    axis.text.x = element_text(),
    axis.text=element_text(face="bold"),
    axis.ticks=element_line(size=1),
    plot.background=element_blank(),
    panel.border=element_blank()
  ) 
```

```{r}
categoryCrimeGrid <- finalCrimeData %>% 
  group_by(location, category) %>% 
  summarise(numberOfCrimes2 = n()) 
```

```{r}
ggplot(categoryCrimeGrid,aes(x=category,y=location, fill=numberOfCrimes2))+
  geom_tile(colour="white",size=0.25)+
  labs(x="",y="")+
  scale_y_discrete(expand=c(0,0))+
  scale_fill_viridis(option = "B", name = "Number of crimes") +
  coord_fixed()+
  theme_grey(base_size=8)+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.text=element_text(face="bold"),
    axis.ticks=element_line(size=0.4),
    plot.background=element_blank(),
    panel.border=element_blank()
  ) #+
```
























```{r}
finalCrimeData$location.latitude <- as.numeric(finalCrimeData$location.latitude)
finalCrimeData$location.longitude <- as.numeric(finalCrimeData$location.longitude)
```

```{r}
length(finalCrimeData$location)
```


```{r}
augustData <- finalCrimeData %>%
  filter(date == "2018-08") %>% 
  sample_frac(.1)

firstDecemberData <- finalCrimeData %>%
  filter(date == "2017-12") %>% 
  sample_frac(.1)

secondDecemberData <- finalCrimeData %>%
  filter(date == "2018-12") %>% 
  sample_frac(.1)

```

```{r}
head(firstDecemberData)
head(secondDecemberData)
head(augustData)
```




```{r}
color_scheme <- viridis::cividis(n_distinct(firstDecemberData$category))
pal = colorFactor(color_scheme, firstDecemberData$category)

firstDecemberData %>% 
  leaflet() %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  addCircleMarkers(~as.numeric(location.longitude),
                   ~as.numeric(location.latitude),
                   fillColor = ~pal(category),
                   stroke = FALSE, fillOpacity = 0.8,
                   clusterOptions = markerClusterOptions(), # adds summary circles
                   popup = ~as.character(category)
  )
```





```{r}
color_scheme <- viridis::cividis(n_distinct(augustData$category))
pal = colorFactor(color_scheme, augustData$category)

augustData %>% 
  leaflet() %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  addCircleMarkers(~as.numeric(location.longitude),
                   ~as.numeric(location.latitude),
                   fillColor = ~pal(category),
                   stroke = FALSE, fillOpacity = 0.8,
                   clusterOptions = markerClusterOptions(), # adds summary circles
                   popup = ~as.character(category)
  )
```


```{r}
color_scheme <- viridis::cividis(n_distinct(secondDecemberData$category))
pal = colorFactor(color_scheme, secondDecemberData$category)

secondDecemberData %>% 
  leaflet() %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  addCircleMarkers(~as.numeric(location.longitude),
                   ~as.numeric(location.latitude),
                   fillColor = ~pal(category),
                   stroke = FALSE, fillOpacity = 0.8,
                   clusterOptions = markerClusterOptions(), # adds summary circles
                   popup = ~as.character(category)
  )
```




clusteredMap <- leaflet(data = firstDecemberData)
clusteredMap <- addTiles(clusteredMap)
clusteredMap <- addMarkers(clusteredMap,~location.longitude,~location.latitude,clusterOptions = markerClusterOptions(),popup = ~category)
clusteredMap

clusteredMap2 <- leaflet(data = secondDecemberData)
clusteredMap2 <- addTiles(clusteredMap)
clusteredMap2 <- addMarkers(clusteredMap,~location.longitude,~location.latitude,clusterOptions = markerClusterOptions(),popup = ~category)
clusteredMap2

clusteredMap3 <- leaflet(data = augustData)
clusteredMap3 <- addTiles(clusteredMap)
clusteredMap3 <- addMarkers(clusteredMap,~location.longitude,~location.latitude,clusterOptions = markerClusterOptions(),popup = ~category)





